Fig3

### 2020-02-10 analysis/figure-1.Rmd
attempt to combine all three figs

source("../R/themes.R")

@@

# Figure 1. Experimental design and tSNE analysis

## wrange data

```{r wrangle}
source("../R/wrangledata.R")
```

@@

```{r fig1, fig.width=7}

plottsneelipse <- function(tsnedf, whichfactor, whichcolors){
  p <- ggplot(tsnedf, aes(x = V1, y = V2)) +
    geom_point(size = 1, aes(color = whichfactor)) +
    theme_B3() +
    labs(x = "tSNE 1", y = "tSNE 2") +
    scale_color_manual(values = whichcolors) +
    theme(legend.position = "none",
          axis.text = element_blank()) +
    stat_ellipse(linetype = 2, aes(color = tissue )) 
  return(p)
}

a <- plottsneelipse(chartsne, chartsne$tissue, allcolors) + labs(subtitle = "tissue\n")    
b <- plottsneelipse(chartsne, chartsne$sex, allcolors)   + labs(y = " ", subtitle = "tissue * sex\n")    
c <- plottsneelipse(ftsne, ftsne$treatment, allcolors ) + labs(y = " ", subtitle = "females\ntissue * treatment")
d <- plottsneelipse(mtsne, mtsne$treatment, allcolors ) + labs(y = " ", subtitle = "males\ntissue * treatment")

@@

fig1 <- plot_grid(expdesign, abcd, nrow = 2, labels = c("a", "b"), label_size = 12, rel_heights = c(0.5,1))
fig1
```

>>>>

source("../R/themes.R")
source("../R/functions.R")
source("../R/wrangledata.R")

@@

# Figure 1. Experimental design, tSNE analysis, PCA, and prolactin

@@

```{r }

plottsneelipse <- function(tsnedf, pointcolor, whichcolors){
  p <- ggplot(tsnedf, aes(x = V1, y = V2)) +
    geom_point(size = 1, aes(color = pointcolor)) +
    theme_B3() +
    labs(x = "tSNE 1", y = "tSNE 2") +
    scale_color_manual(values = whichcolors) +
    theme(legend.position = "none",
          axis.text = element_blank()) +
    stat_ellipse(linetype = 2, aes(color = tissue )) 
  return(p)
}

a <- plottsneelipse(chartsne, chartsne$tissue, allcolors) + labs(subtitle = "tissue\n")    
b <- plottsneelipse(chartsne, chartsne$sex, allcolors)   + labs(y = " ", subtitle = "tissue * sex\n")    
c <- plottsneelipse(ftsne, ftsne$treatment, allcolors ) + labs(y = " ", subtitle = "treatment * tissue\nfemales")
d <- plottsneelipse(mtsne, mtsne$treatment, allcolors ) + labs(y = " ", subtitle = "treatment * tissue\nmales")

@@

abcde <- plot_grid(expdesign, abcd, nrow = 2, labels = c("a", "b"), label_size = 12, rel_heights = c(0.5,1))
abcde
```

## pca

```{r supplfig1}
charpca <- subsetmakepca(tissuelevels, charlevels, sexlevels)	
charfviz <- makefvizdf(tissuelevels, charlevels, sexlevels)

f <- plotcolorfulpcs(charpca,charpca$treatment, allcolors) + labs(subtitle = " ") +
  theme(legend.position = c(0.6,0.2), 
        #legend.direction = "horizontal", 
        legend.key.size = unit(0.5, 'lines')) + 
  guides(color = FALSE) +
  labs(subtitle = "tissue * treatment")   
g <- plotfriz(charfviz) + labs(subtitle = "  ")

pcaplots <- plot_grid(f,g, labels = c("f", "g"), label_size = 12, align = "hv")
pcaplots
```

## PRL

```{r}
PRLplot <- plotprolactin(PRLpit, PRLpit$counts, "PRL", "treatment * sex, pituitary only") + 
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1), 
        axis.title.x = element_blank(),
        axis.title.y = element_text(face = "italic"))

fgh <- plot_grid(pcaplots, PRLplot, labels = c(" ", "h"), label_size = 12)
fgh
```

## all together now

```{r fig1, fig.width=7, fig.height=6}
plot_grid(abcde, fgh, nrow = 2, rel_heights = c(2,1.5))
```

### 2020-02-10 analysis/figure-3.Rmd
attempt to combine all three figs

vsd_path <- "../results/DEseq2/"   # path to the data
vsd_files <- dir(vsd_path, pattern = "*vsd.csv") # get file names
vsd_pathfiles <- paste0(vsd_path, vsd_files)
vsd_files

PRLvsd <- vsd_pathfiles %>%
  setNames(nm = .) %>% 
  map_df(~read_csv(.x), .id = "file_name")  %>% 
  dplyr::rename("gene" = "X1") %>% 
  pivot_longer(cols = L.G118_female_gonad_control:y98.o50.x_male_pituitary_inc.d3, 
               names_to = "samples", values_to = "counts") %>%
  filter(gene == "PRL")  %>%
  dplyr::mutate(sextissue = sapply(strsplit(file_name, '_vsd.csv'), "[", 1)) %>%
  dplyr::mutate(sextissue = sapply(strsplit(sextissue, '../results/DEseq2/'), "[", 2)) %>%
  dplyr::mutate(sex = sapply(strsplit(sextissue, '\\_'), "[", 1),
                tissue = sapply(strsplit(sextissue, '\\_'), "[", 2),
                treatment = sapply(strsplit(samples, '\\_'), "[", 4)) %>%
  dplyr::mutate(treatment = sapply(strsplit(treatment, '.NYNO'), "[", 1)) %>%
  dplyr::select(sex, tissue, treatment, gene, samples, counts)

PRLvsd$treatment <- factor(PRLvsd$treatment, levels = alllevels)

PRLhyp <- PRLvsd %>% filter(tissue == "hypothalamus")
PRLpit <- PRLvsd %>% filter(tissue == "pituitary")
PRLgon <- PRLvsd %>% filter(tissue == "gonad")
```

```{r fig3, fig.width=7}
plotprolactin <- function(df, myy, myylab, mysubtitle ){

  p <-  ggplot(df, aes(x = treatment, y = myy)) +
    geom_boxplot(aes(fill = treatment, color = sex)) +
    theme_B3() +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = sexcolors) +
    labs(y = "prolactin (ng/mL)", x = NULL) +
    theme(legend.position = c(0.85,0.15), legend.direction = "horizontal") + 
  labs(x = "parental stage", subtitle = mysubtitle, y= myylab) +
      guides(fill = guide_legend(nrow = 1)) 
  return(p)
}

>>>>

```

```{r fig3, fig.width=7}
